---
title: "flawless_code_public_part2"
author: "Owen Forbes"
date: "06/10/2023"
output: html_document
---

# Part 2 - Code accompanying paper "Functional analysis within latent states: A novel framework for analysing functional time series data"



#---


Relating FHMM dominants states, (and eventually FPCs within states of interest), to key health outcomes and demographics

(Demographics)
- Sex
- Age
- Handedness

(Health outcomes)
- depressive symptoms (MFQ parent report) 
# Could make sense to check correlation between parent-report and self-report if going with parent-report for everybody...  wait and see how age relationship to states looks
- anxiety symptoms (SCARED parent report)
- positive affect (PANAS - self report)
- negative affect (PANAS - self report)

- cognitive function (NIH scores)

- global functioning? (CGAS clinician rated)

-----------------


----------------
STEPS


1. import health & demographic data
2. import FHMM results
3. Calculate Viterbi dominant states, matched against study IDs 
4. Create DF with dominant state, and outcome measures
5. generate box plots and histograms for each outcome




```{r}
library(tidyverse)
library(ggplot2)
```



#----------








```{r}

# subset demog_health_df by ages 9-15

load("index_1158_ages_915")

load("demog_health_df_280223") #280223 - added YSR and WISC-V


demog_health_df_915 <- demog_health_df[index_1158_ages_915,]

psych::describe(demog_health_df_915)
```



# EXPLORING RESULTS BY FHMM AGES 9-15



2. import FHMM results



# EXPLORATORY ANALYSIS FOR ALL AGES MODEL (5-21)
```{r}

load("/Volumes/Owen_SSD/CMIhbn_data/Analysis_Outputs/fit_fhmm_4state_ages915_initialised")

estimated_fhmm_states_4_915 <- hmmhdd::viterbi(fit_fhmm_4state_ages915_initialised)

#--------------


fpc_s1_gg <- ggplot()+
  geom_hline(yintercept = 0,colour="black")+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s1$harmonics$coefs[1:58,5],colour="FPC 5"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s1$harmonics$coefs[1:58,4],colour="FPC 4"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s1$harmonics$coefs[1:58,3],colour="FPC 3"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s1$harmonics$coefs[1:58,2],colour="FPC 2"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s1$harmonics$coefs[1:58,1],colour="FPC 1"))+
  ylim(-0.6,0.6)+xlab("Frequency (Hz)")+theme_bw(base_size=14)+ylab("") +  scale_colour_viridis(name="Functional PCs", option = "turbo", discrete=T, direction = -1, begin = 0.15, end = 0.85)


gg_fhmm_selected_4_initial_915<- ggplot()+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fit_fhmm_4state_ages915_initialised$centroids$data[[1]][1,],colour="State 1"))+ #1 most occupied - high delta, very low alpha, high upper beta
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fit_fhmm_4state_ages915_initialised$centroids$data[[1]][2,],colour="State 3"))+ # 3 most occupied - high freq moderate alpha, high lower beta
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fit_fhmm_4state_ages915_initialised$centroids$data[[1]][3,],colour="State 2"))+ #2 most occupied - high theta, low freq moderate alpha, low beta
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fit_fhmm_4state_ages915_initialised$centroids$data[[1]][4,],colour="State 4"))+ #4 least occupied - very high alpha
  ylim(0,1.1) + ggtitle ("Centroids for 4 latent states from functional Hidden Markov model") + ylab("Power (uV^2/Hz)") +xlab("Frequency (Hz)")+theme_bw(base_size=14) + #scale_colour_manual(breaks=c(1,3,2,4),labels=c(1,2,3,4))
 scale_colour_viridis(name="", option = "turbo", discrete=T, direction = -1, begin = 0.15, end = 0.85)#scale_colour_manual(name  ="Latent States",
                            #breaks=c(1,3,2,4),
                            #labels=c("State 1", "State 2", "State 3", "State 4"))
#hist(estimated_fhmm_states_4_915)

estimated_fhmm_states_4_915
#gg_fhmm_selected_4_initial
gg_fhmm_selected_4_initial_915

# transition matrix
fit_fhmm_4state_ages915_initialised$A


#!!!!!!!!!!!!
# NEED TO REJIG PLOTTING DATA FRAME to get legend for state labels... Put centroids into new data frame

# SWITCH LABELS FOR STATES 2 and 3

#!!!!!!!!!!!
tiff("FHMM_centroids_230423.tif", compression = "lzw",width = 900, height = 600, pointsize = 12)
gg_fhmm_selected_4_initial_915
dev.off()  


```


2. Calculate Viterbi dominant states... Add to demog_health_df


```{r}

viterbi_matrix_915 <- t(matrix(estimated_fhmm_states_4_915,ncol = 503)) #stacks vertically - so start with 503 columns, and transpose

dim(viterbi_matrix_915)
#[1] 503  180 ---- 180 obs per person -- 5*40 seconds of eyes closed PSDs one per second, losing 4 seconds from each (head and tail 2 seconds)


viterbi_df_for_psychdescribe_915 <- data.frame(t(viterbi_matrix_915))

psych::describe(viterbi_df_for_psychdescribe_915)




viterbi_df_915 <- data.frame(viterbi_matrix_915)

viterbi_df_915$EID <- demog_health_df_915$EID


```


```{r}



#!!!!!!!!!!!

# SWITCH LABELS FOR STATES 2 and 3 HERE

viterbi_df_915[viterbi_df_915 == 2] <- "temp"
viterbi_df_915[viterbi_df_915 == 3] <- 2
viterbi_df_915[viterbi_df_915 == "temp"] <- 3


#!!!!!!!!!!!


estimated_fhmm_states_4_915

estimated_fhmm_states_4_915[estimated_fhmm_states_4_915 == 2] <- "temp"
estimated_fhmm_states_4_915[estimated_fhmm_states_4_915 == 3] <- 2
estimated_fhmm_states_4_915[estimated_fhmm_states_4_915 == "temp"] <- 3


#!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!



```

```{r}

viterbi_df_915$dominant_state <- apply(viterbi_df_915,1,function(x) names(which.max(table(x))))
viterbi_df_915$dominant_proportion <- rep(NA, length(viterbi_df_915$X1))

for(i in 1:503){
  viterbi_df_915$dominant_proportion[i] <- sum(viterbi_df_915[i,1:180]==viterbi_df_915$dominant_state[i],na.rm = T)/180
}



psych::describe(viterbi_df_915$dominant_proportion) #lowest = 0.34! rapidly switching 

hist(viterbi_df_915$dominant_proportion,breaks=25) #modes at 0.6, 0.8 because **tendency to spend all of one EC segment in one state** according to FHMM


# Needed to fix this below - was adding + onto n_states_visited for states 2-4
viterbi_df_915$visits_1 <- apply(viterbi_df_915[,1:180],MARGIN = 1,function(x) ifelse(1 %in% x,1,0))
viterbi_df_915$visits_2 <- apply(viterbi_df_915[,1:180],MARGIN = 1,function(x) ifelse(2 %in% x,1,0))
viterbi_df_915$visits_3 <- apply(viterbi_df_915[,1:180],MARGIN = 1,function(x) ifelse(3 %in% x,1,0))
viterbi_df_915$visits_4 <- apply(viterbi_df_915[,1:180],MARGIN = 1,function(x) ifelse(4 %in% x,1,0))
  
  
  
  
  

hist(as.numeric(viterbi_df_915$dominant_state),breaks=5)
# viterbi_df[which.min(viterbi_df$dominant_proportion),] --> rapid switching between 4, 3, and 1



# ALSO CALCULATE...

# N of states
# N of transitions
# percent of time in each state


viterbi_df_915$n_states_visited <- (viterbi_df_915$visits_1 + viterbi_df_915$visits_2 + viterbi_df_915$visits_3 + viterbi_df_915$visits_4)

viterbi_df_915$n_transitions_within_EC <- (apply(viterbi_df_915[,1:36],1,function(x) sum(ifelse(x != lag(x) | is.na(lag(x)), 1, 0))-1) +
                                    apply(viterbi_df_915[,1*36+(1:36)],1,function(x) sum(ifelse(x != lag(x) | is.na(lag(x)), 1, 0))-1) +
                                    apply(viterbi_df_915[,2*36+(1:36)],1,function(x) sum(ifelse(x != lag(x) | is.na(lag(x)), 1, 0))-1) +
                                    apply(viterbi_df_915[,3*36+(1:36)],1,function(x) sum(ifelse(x != lag(x) | is.na(lag(x)), 1, 0))-1) +
                                    apply(viterbi_df_915[,4*36+(1:36)],1,function(x) sum(ifelse(x != lag(x) | is.na(lag(x)), 1, 0))-1)) # count transitions, minus 1 as it counts the first entry as 1, within 5 36 second windows
# 

viterbi_df_915$n_transitions_all <- (apply(viterbi_df_915[,1:180],1,function(x) sum(ifelse(x != lag(x) | is.na(lag(x)), 1, 0))-1)) #include transitions within and between EC segments

viterbi_df_915$s1_percent <- apply(viterbi_df_915,MARGIN = 1,function(x) sum(x[1:180] == 1)/180)
viterbi_df_915$s2_percent <- apply(viterbi_df_915,MARGIN = 1,function(x) sum(x[1:180] == 2)/180)
viterbi_df_915$s3_percent <- apply(viterbi_df_915,MARGIN = 1,function(x) sum(x[1:180] == 3)/180)
viterbi_df_915$s4_percent <- apply(viterbi_df_915,MARGIN = 1,function(x) sum(x[1:180] == 4)/180)



view(viterbi_df_915)


hist(viterbi_df_915$n_states_visited)

hist(viterbi_df_915$s1_percent) #s1 is main state where people are there 100% - others are mostly mixed
hist(viterbi_df_915$s2_percent)
hist(viterbi_df_915$s3_percent)
hist(viterbi_df_915$s4_percent)




hist1 <- hist(as.numeric(viterbi_df_915$dominant_state),main="Number of individuals for whom each state is dominant", xlab = "Functional Latent States", ylab = "Number of individuals")


hist2 <- hist(viterbi_df_915$n_states_visited, main = "Histogram of number of states visited")


hist3 <- hist(viterbi_df_915$n_transitions_all, main = "Histogram of number of transitions between states")



png("histograms_170323.png", width = 700, height = 1500, pointsize = 18)
par(mfrow= c(3, 1))
hist(as.numeric(viterbi_df_915$dominant_state),main="Number of individuals for whom each state is dominant", xlab = "Functional Latent States", ylab = "Number of individuals")
hist(viterbi_df_915$n_states_visited, main = "Histogram of number of states visited")
hist(viterbi_df_915$n_transitions_all, main = "Histogram of number of transitions between states")
dev.off()  


#-------

# Trying using GGPLOT

hist1 <- ggplot(viterbi_df_915, aes(x = as.numeric(dominant_state))) +
  geom_histogram(binwidth = 1,col="black", fill = "lightgrey") +
  labs(title = "Number of individuals for whom each FHMM latent state is dominant",
       x = "Dominant State",
       y = "Number of individuals")+theme_bw()

hist2 <- ggplot(viterbi_df_915, aes(x = n_states_visited)) +
  geom_histogram(binwidth = 1,col="black", fill = "lightgrey") +
  labs(title = "Number of FHMM latent states visited",
       x = "Number of States Visited",
       y = "Count")+theme_bw()

hist3 <- ggplot(viterbi_df_915, aes(x = n_transitions_all)) +
  geom_histogram(binwidth = 1,col="black", fill = "lightgrey") +
  labs(title = "Number of transitions between FHMM latent states",
       x = "Number of Transitions",
       y = "Count")+
scale_x_continuous(breaks = seq(0, 8, 1), lim = c(-0.5, 8.5))+theme_bw()


ggsave("histograms_230423.png", 
       grid.arrange(hist1, hist2, hist3, ncol = 1, nrow = 3),
       width = 7, height = 15, dpi = 300, units = "in")


#-------

sum(viterbi_df_915$n_states_visited==1)

234/503

sum(viterbi_df_915$n_states_visited==2)

205/503


sum(viterbi_df_915$n_transitions_all < 5)

479/503

```






```{r}

subset_viterbi_bits_915 <- viterbi_df_915[,181:ncol(viterbi_df_915)]

demog_health_states_df_915 <- left_join(demog_health_df_915,subset_viterbi_bits_915,by="EID")

ncol(demog_health_states_df_915) #23

demog_health_states_df_915 <- demog_health_states_df_915 %>% mutate_at(c(2:ncol(demog_health_states_df_915)),as.numeric)


# raw scores
demog_health_states_df_915 %>% group_by(dominant_state) %>% summarise(across(everything(), list(mean=mean, sd=sd, range=range), na.rm=TRUE))

# Z-scores
demog_health_states_df_915 %>% mutate_at(c(5:25),scale) %>% group_by(dominant_state) %>% summarise(across(everything(), list(mean=mean), na.rm=TRUE))

gg_fhmm_selected_4_initial_915





#------  

# test for dominant state group differences with ANOVA (or other?) for age, sex, handedness
# no sig between group diffs

aov_df_filter <- demog_health_states_df_915 %>% filter(dominant_proportion > 0.8)

age_anova <- aov(Age ~ dominant_state, data = aov_df_filter)
summary(age_anova)

sex_anova <- aov(Sex ~ dominant_state, data = aov_df_filter)
summary(sex_anova)

hand_anova <- aov(EHQ_Total ~ dominant_state, data = aov_df_filter)
summary(hand_anova)



#------- Trimming down outcome measures

demog_health_states_df_915_fewer_outcomes <- demog_health_states_df_915[,-c(6:10,16,17,20:25)]#-c(6:10,12:15,20:24)]

view(demog_health_states_df_915_fewer_outcomes)

#--------

# raw scores compare by dominant state
compare_raw_scores <- demog_health_states_df_915_fewer_outcomes %>% group_by(dominant_state) %>% summarise(across(everything(), list(mean=mean), na.rm=TRUE))

# z-scores compare by dominant state

compare_z_scores <- demog_health_states_df_915_fewer_outcomes %>% mutate_at(c(5:12),scale) %>% group_by(dominant_state) %>% summarise(across(everything(), list(mean=mean), na.rm=TRUE))


view(compare_raw_scores)
view(compare_z_scores)


descriptive_stats_all <-  demog_health_states_df_915_fewer_outcomes %>% summarise(across(everything(), list(mean=mean, sd = sd), na.rm=TRUE))
view(descriptive_stats_all)


#-------- Compare only ppl who spend >80% in dominant state
compare_raw_scores_dominant80 <- demog_health_states_df_915_fewer_outcomes %>% filter(dominant_proportion >= 0.8) %>% group_by(dominant_state) %>% summarise(across(everything(), list(mean=mean, sd = sd), na.rm=TRUE))
view(compare_raw_scores_dominant80)

compare_z_scores_dominant80 <- demog_health_states_df_915_fewer_outcomes %>% filter(dominant_proportion >= 0.8) %>% mutate_at(c(5:12),scale) %>% group_by(dominant_state) %>% summarise(across(everything(), list(mean=mean), na.rm=TRUE))
view(compare_z_scores_dominant80)


count_greater_80 <- demog_health_states_df_915_fewer_outcomes %>% filter(dominant_proportion > 0.8)
#length(count_greater_80$dominant_state) #281 individuals > 0.8; 353 >= 0.8

```


#---------


# gtsummary tables

```{r}
# Trying with gtsummary
library(gtsummary)
library(gt)

gt_data <- demog_health_states_df_915_fewer_outcomes %>% relocate(c(5:6), .after = 10) %>%  rename(Cog_NIH7_Card = NIH7_Card,Cog_NIH7_Flanker = NIH7_Flanker,Cog_NIH7_List = NIH7_List,Cog_NIH7_Pattern = NIH7_Pattern)



# overall

overall_gt <- gt_data  %>% select(c(2:12)) %>%
    tbl_summary(
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    digits = everything() ~ 1,
      missing="no"
    ) %>% 
 add_n() %>% 
    modify_header(label = "**Dominant State (>= 80%)**")
  #gtsummary::as_gt() %>%
  #gt::as_latex()


# 80% dominant


dominant_state_gt <- gt_data  %>% filter(dominant_proportion >= 0.8) %>% select(c(2:13)) %>%
    tbl_summary(
    by = dominant_state,
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    digits = everything() ~ 1,
      missing="no"
    ) %>% 
     modify_header(label = "**Dominant State (>= 80%)**")
  # gtsummary::as_gt() %>%
  # gt::as_latex()


# Combine them
combined_gt <- tbl_merge(list(overall_gt,dominant_state_gt),tab_spanner = F) %>% 
  modify_table_body(
    mutate,
    groupname_col = case_when(variable %in% c("Sex","Age","EHQ_Total") ~ "Demographics",
                              variable %in% c("Cog_NIH7_Card","Cog_NIH7_Flanker","Cog_NIH7_List","Cog_NIH7_Pattern") ~ "Cognitive Function",
                              variable %in% c("YSR_Ext_T","YSR_Int_T","MFQ_SR_Total..1","SCARED_SR_Total") ~ "Psychopathology")
  )


combined_gt %>% 
  gtsummary::as_gt() %>%
  gt::as_raw_html()


  
  
  
  
```


```{r}
#---------

# How many at each level?

#sum(demog_health_states_df_915_fewer_outcomes$dominant_proportion > 0.8) #281
#sum(demog_health_states_df_915_fewer_outcomes$dominant_proportion >= 0.8) #353
#sum(demog_health_states_df_915_fewer_outcomes$dominant_proportion > 0.6) #407
#sum(demog_health_states_df_915_fewer_outcomes$dominant_proportion >= 0.6) #458

sum(demog_health_states_df_915_fewer_outcomes$dominant_proportion >= 0.8) #353
length(demog_health_states_df_915_fewer_outcomes$EID) #503

sum(demog_health_states_df_915_fewer_outcomes$dominant_proportion <= 0.6) #96
sum(demog_health_states_df_915_fewer_outcomes$dominant_proportion <= 0.5) #17



sum(demog_health_states_df_915_fewer_outcomes$s2_percent > 0.8) #36
sum(demog_health_states_df_915_fewer_outcomes$s2_percent >= 0.8) #52
sum(demog_health_states_df_915_fewer_outcomes$s2_percent > 0.6) #60
sum(demog_health_states_df_915_fewer_outcomes$s2_percent >= 0.6) #71


#------

sum(demog_health_states_df_915_fewer_outcomes$s2_percent > 0.8) #36
sum(demog_health_states_df_915_fewer_outcomes$s2_percent >= 0.8) #52
sum(demog_health_states_df_915_fewer_outcomes$s2_percent > 0.6) #60
sum(demog_health_states_df_915_fewer_outcomes$s2_percent >= 0.6) #71



#-------

sum(demog_health_states_df_915_fewer_outcomes$dominant_state==1) #213
sum(demog_health_states_df_915_fewer_outcomes$dominant_state==2) #79
sum(demog_health_states_df_915_fewer_outcomes$dominant_state==3) #139
sum(demog_health_states_df_915_fewer_outcomes$dominant_state==4) #72


#------


sum(demog_health_states_df_915_fewer_outcomes$s1_percent>=0.8) #167
sum(demog_health_states_df_915_fewer_outcomes$s2_percent>=0.8) #90
sum(demog_health_states_df_915_fewer_outcomes$s3_percent>=0.8) #52
sum(demog_health_states_df_915_fewer_outcomes$s4_percent>=0.8) #44


```



#---------------

Fingerprint plots


```{r}

# Rename NIH vars to start with "Cog" for alphabetic order of plots

demog_health_states_df_915_fewer_outcomes_fingerprints <- demog_health_states_df_915_fewer_outcomes %>% rename(Cog_NIH7_Card = NIH7_Card,Cog_NIH7_Flanker = NIH7_Flanker,Cog_NIH7_List = NIH7_List,Cog_NIH7_Pattern = NIH7_Pattern)

# NB z-scores relative to WHOLE GROUP, not subset -- scale before filter
compare_z_scores_dominant80 <- demog_health_states_df_915_fewer_outcomes_fingerprints %>% mutate_at(c(5:12),scale) %>% filter(dominant_proportion >= 0.8)  %>% group_by(dominant_state) %>% summarise(across(everything(), list(mean=mean), na.rm=TRUE))


compare_z_scores_plots_df <- compare_z_scores_dominant80 %>% pivot_longer(cols = c(6:13),names_to = "health_measures",values_to = "z_scores")

compare_z_scores_plots_80 <- ggplot(compare_z_scores_plots_df, aes(x=health_measures, y=z_scores, group=health_measures)) + 
  geom_col(aes(fill=health_measures))+
  scale_fill_manual(values=viridis::turbo(9,direction = -1), labels=c("NIH Card", "NIH Flanker", "NIH List", "NIH Pattern", "MFQ SR", "SCARED SR", "YSR Ext", "YSR Int"))+
  #scale_fill_manual(values=viridis::turbo(9,direction = -1))+#turbo(9,direction = -1)[2:9])
  #scale_fill_brewer(palette="Dark2") +
  guides(fill=guide_legend(title="Health Measures"))+
  facet_grid(. ~ dominant_state)+
  theme_bw()+
  theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
  theme(panel.spacing = unit(2, "lines"))+
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  xlab("FHMM Dominant State (>= 80%)")+
  ylab("Z-Scores") + theme(text = element_text(size = 18))#+ylim(c(-0.25,0.25))
  
compare_z_scores_plots_80



compare_z_scores_all <- demog_health_states_df_915_fewer_outcomes_fingerprints %>% mutate_at(c(5:12),scale) %>% group_by(dominant_state) %>% summarise(across(everything(), list(mean=mean), na.rm=TRUE))


compare_z_scores_plots_all_df <- compare_z_scores_all %>% pivot_longer(cols = c(6:13),names_to = "health_measures",values_to = "z_scores")

compare_z_scores_plots_all <- ggplot(compare_z_scores_plots_all_df, aes(x=health_measures, y=z_scores, group=health_measures)) + 
  geom_col(aes(fill=health_measures))+
  #scale_fill_manual(values=viridis::turbo(9,direction = -1)[2:9])+
  scale_fill_manual(values=viridis::turbo(9,direction = -1), labels=c("NIH Card", "NIH Flanker", "NIH List", "NIH Pattern", "MFQ SR", "SCARED SR", "YSR Ext", "YSR Int"))+#turbo(9,direction = -1)[2:9])
  #scale_fill_brewer(palette="Dark2") +
  guides(fill=guide_legend(title="Health Measures"))+
  facet_grid(. ~ dominant_state)+
  theme_bw()+
  theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
  theme(panel.spacing = unit(2, "lines"))+
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  xlab("FHMM Dominant State (ALL participants)")+
  ylab("Z-Scores") + theme(text = element_text(size = 18)) #+ylim(c(-0.25,0.25))
  
compare_z_scores_plots_all

# 
# 
# png("fingerprint_plots.png",width=1000,height=1000,pointsize=14)
#   grid.arrange(eeg_fingerprint_plots,health_fingerprint_plots)
# dev.off()







#compare_z_scores_plots_all
compare_z_scores_plots_80



# Save as TIFF

tiff("FHMM_fingerprints_100323.tif", compression = "lzw",width = 800, height = 600, pointsize = 12)
compare_z_scores_plots_80
dev.off()  

```




# VENN DIAGRAM for state visiting

```{r}

library(ggvenn)


venn_df <- demog_health_states_df_915_fewer_outcomes %>% mutate(`State 1` = visits_1==1,`State 2` = visits_2==1,`State 3` = visits_3==1,`State 4` = visits_4==1)

venn_plot <- ggvenn(venn_df,c("State 1","State 2","State 3","State 4"),
  #fill_color = c("#0073C2FF", "#EFC000FF", "#868686FF", "#CD534CFF"),
  #fill_color = viridis::turbo(9, direction = -1)[c(1,4,6,9)],
  stroke_size = 0.5, set_name_size = 10, text_size=5.5
  )



tiff("FHMM_Venn_100323.tif", compression = "lzw",width = 800, height = 600, pointsize = 12)
venn_plot
dev.off()  


```















#----------------



# More detailed exploration within states

* Run FPCA within each state
--> AVERAGE each individual's loadings across all 1-second PSDs they spend in that state?



- calculate further Viterbi features
-- n. states visited
-- n. transitions
-- average visit length?
// Other?




# FPCA within states...

```{r}

load("/Volumes/Owen_SSD/CMIhbn_data/Analysis_Outputs/fooof_ages915_stacked")


library(fda)
library(viridis)

FHMM_915_index_s1 <- which(estimated_fhmm_states_4_915 %in% 1) # red - low alpha
FHMM_915_index_s2 <- which(estimated_fhmm_states_4_915 %in% 2) # green - high freq mod power alpha
FHMM_915_index_s3 <- which(estimated_fhmm_states_4_915 %in% 3) # orange - low freq mod power alpha
FHMM_915_index_s4 <- which(estimated_fhmm_states_4_915 %in% 4) # blue - v high alpha



#------- FPCA by state

#----------- state 1
fooof_s1 <- t(as.matrix(fooof_ages915_stacked)[FHMM_915_index_s1,1:58]) 
fpca_data_s1 <- fda::Data2fd(y=fooof_s1, argvals = c(seq(1.5,30,by=0.5)))
fpca_s1 <- fda::pca.fd(fpca_data_s1, nharm = 8, harmfdPar=fdPar(fpca_data_s1),centerfns=TRUE)

fpca_s1
plot(fpca_s1$harmonics, lwd = 1)
#summary(fpca_s1)
fpca_s1$varprop
plot(fpca_s1$varprop)

cumsum(fpca_s1$varprop)



fpc_s1_gg <- ggplot()+
  geom_hline(yintercept = 0,colour="black")+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s1$harmonics$coefs[1:58,5],colour="FPC 5"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s1$harmonics$coefs[1:58,4],colour="FPC 4"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s1$harmonics$coefs[1:58,3],colour="FPC 3"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s1$harmonics$coefs[1:58,2],colour="FPC 2"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s1$harmonics$coefs[1:58,1],colour="FPC 1"))+
  ylim(-0.6,0.6)+xlab("Frequency (Hz)")+theme_bw(base_size=14)+ylab("") +  scale_colour_viridis(name="Functional PCs", option = "turbo", discrete=T, direction = -1, begin = 0.15, end = 0.85)



#----------- state 2
fooof_s2 <- t(as.matrix(fooof_ages915_stacked)[FHMM_915_index_s2,1:58]) 
fpca_data_s2 <- fda::Data2fd(y=fooof_s2, argvals = c(seq(1.5,30,by=0.5)))
fpca_s2 <- fda::pca.fd(fpca_data_s2, nharm = 8, harmfdPar=fdPar(fpca_data_s2),centerfns=TRUE)

fpca_s2
plot(fpca_s2$harmonics, lwd = 1)
#summary(fpca_s2)
fpca_s2$varprop
plot(fpca_s2$varprop)



fpc_s2_gg <- ggplot()+
  geom_hline(yintercept = 0,colour="black")+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s2$harmonics$coefs[1:58,5],colour="FPC 5"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s2$harmonics$coefs[1:58,4],colour="FPC 4"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s2$harmonics$coefs[1:58,3],colour="FPC 3"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s2$harmonics$coefs[1:58,2],colour="FPC 2"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s2$harmonics$coefs[1:58,1],colour="FPC 1"))+
  ylim(-0.6,0.6)+xlab("Frequency (Hz)")+theme_bw(base_size=14)+ylab("") +  scale_colour_viridis(name="Functional PCs", option = "turbo", discrete=T, direction = -1, begin = 0.15, end = 0.85)



#----------- state 3
fooof_s3 <- t(as.matrix(fooof_ages915_stacked)[FHMM_915_index_s3,1:58]) 
fpca_data_s3 <- fda::Data2fd(y=fooof_s3, argvals = c(seq(1.5,30,by=0.5)))
fpca_s3 <- fda::pca.fd(fpca_data_s3, nharm = 8, harmfdPar=fdPar(fpca_data_s3),centerfns=TRUE)

fpca_s3
plot(fpca_s3$harmonics, lwd = 1)
#summary(fpca_s3)
fpca_s3$varprop
plot(fpca_s3$varprop)

cumsum(fpca_s3$varprop)



fpc_s3_gg <- ggplot()+
  geom_hline(yintercept = 0,colour="black")+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s3$harmonics$coefs[1:58,5],colour="FPC 5"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s3$harmonics$coefs[1:58,4],colour="FPC 4"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s3$harmonics$coefs[1:58,3],colour="FPC 3"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s3$harmonics$coefs[1:58,2],colour="FPC 2"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s3$harmonics$coefs[1:58,1],colour="FPC 1"))+
  ylim(-0.6,0.6)+xlab("Frequency (Hz)")+theme_bw(base_size=14)+ylab("") +  scale_colour_viridis(name="Functional PCs", option = "turbo", discrete=T, direction = -1, begin = 0.15, end = 0.85)


#----------- state 4
fooof_s4 <- t(as.matrix(fooof_ages915_stacked)[FHMM_915_index_s4,1:58]) 
fpca_data_s4 <- fda::Data2fd(y=fooof_s4, argvals = c(seq(1.5,30,by=0.5)))
fpca_s4 <- fda::pca.fd(fpca_data_s4, nharm = 8, harmfdPar=fdPar(fpca_data_s4),centerfns=TRUE)

fpca_s4
plot(fpca_s4$harmonics, lwd = 1)
#summary(fpca_s4)
fpca_s4$varprop
plot(fpca_s4$varprop)



fpc_s4_gg <- ggplot()+
  geom_hline(yintercept = 0,colour="black")+
  #geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s4$harmonics$coefs[1:58,6]),colour="purple")+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s4$harmonics$coefs[1:58,5],colour="FPC 5"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s4$harmonics$coefs[1:58,4],colour="FPC 4"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s4$harmonics$coefs[1:58,3],colour="FPC 3"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s4$harmonics$coefs[1:58,2],colour="FPC 2"))+
  geom_line(aes(x=c(seq(1.5,30,by=0.5)),y=fpca_s4$harmonics$coefs[1:58,1],colour="FPC 1"))+
  ylim(-0.6,0.6)+xlab("Frequency (Hz)")+theme_bw(base_size=14)+ylab("") +  scale_colour_viridis(name="Functional PCs", option = "turbo", discrete=T, direction = -1, begin = 0.15, end = 0.85)




#FPCA PLOTS



plot(fpca_s1$varprop)
plot(cumsum(fpca_s1$varprop))
fpc_s1_gg

plot(fpca_s2$varprop)
plot(cumsum(fpca_s2$varprop))
fpc_s2_gg

plot(fpca_s3$varprop)
plot(cumsum(fpca_s3$varprop))
fpc_s3_gg


plot(fpca_s4$varprop)
plot(cumsum(fpca_s4$varprop))
fpc_s4_gg


fpc_s1_gg
fpc_s2_gg
fpc_s3_gg
fpc_s4_gg



#---------

# Exploring structure of FPCA results

#str(fpca_s1)

# SCORES


tiff("FPCA_harmonics_s1_130423.tif", compression = "lzw",width = 1000, height = 600, pointsize = 12)
fpc_s1_gg
dev.off()  



tiff("FPCA_harmonics_s2_130423.tif", compression = "lzw",width = 1000, height = 600, pointsize = 12)
fpc_s2_gg
dev.off()  


tiff("FPCA_harmonics_s3_130423.tif", compression = "lzw",width = 1000, height = 600, pointsize = 12)
fpc_s3_gg
dev.off()  


tiff("FPCA_harmonics_s4_130423.tif", compression = "lzw",width = 1000, height = 600, pointsize = 12)
fpc_s4_gg
dev.off()  





# SCREE PLOTS
png("s1_fpca_scree.png", width = 900, height = 600, pointsize = 18)
plot(fpca_s1$varprop, xlab = "Functional Principal Component", ylab = "Proportion of Variance Explained", main = "Scree plot for State 1 FPCA")
dev.off()


png("s2_fpca_scree.png", width = 900, height = 600, pointsize = 18)
plot(fpca_s2$varprop, xlab = "Functional Principal Component", ylab = "Proportion of Variance Explained", main = "Scree plot for State 2 FPCA")
dev.off()

png("s3_fpca_scree.png", width = 900, height = 600, pointsize = 18)
plot(fpca_s3$varprop, xlab = "Functional Principal Component", ylab = "Proportion of Variance Explained", main = "Scree plot for State 3 FPCA")
dev.off()

png("s4_fpca_scree.png", width = 900, height = 600, pointsize = 18)
plot(fpca_s4$varprop, xlab = "Functional Principal Component", ylab = "Proportion of Variance Explained", main = "Scree plot for State 4 FPCA")
dev.off()



```




# Calculating mean FPC scores by individual...

- 'scores' matrix - rows = all PSDs in that state (individuals merged together)


- TAKE scores matrix, add column which specifies individual study ID
- group by study ID
- calculate colMeans within individual
--> Gives average loading by individual onto each FPC

```{r}

# Calculate mean FPC scores for each individual by state


# state 1 - 305 visitors

fpc_s1_scores_df <- data.frame(fpca_s1$scores)
names(fpc_s1_scores_df) <- c("fpc1_score","fpc2_score","fpc3_score","fpc4_score","fpc5_score","fpc6_score","fpc7_score","fpc8_score")
names(fpc_s1_scores_df)[1:8] <- paste0("s1_",names(fpc_s1_scores_df[1:8]))
# Add column with study IDs
EID_180_each <- rep(demog_health_states_df_915$EID,each=180)

fpc_s1_scores_df$EID <- EID_180_each[FHMM_915_index_s1]

fpc_s1_score_means <- fpc_s1_scores_df %>% group_by(EID) %>% summarise(across(s1_fpc1_score:s1_fpc8_score, ~ mean(.x))) #colMeans - average loading by individual

#---
# state 2 - 163 visitors

fpc_s2_scores_df <- data.frame(fpca_s2$scores)
names(fpc_s2_scores_df) <- c("fpc1_score","fpc2_score","fpc3_score","fpc4_score","fpc5_score","fpc6_score","fpc7_score","fpc8_score")
names(fpc_s2_scores_df)[1:8] <- paste0("s2_",names(fpc_s2_scores_df[1:8]))

# Add column with study IDs
EID_180_each <- rep(demog_health_states_df_915$EID,each=180)

fpc_s2_scores_df$EID <- EID_180_each[FHMM_915_index_s2]

fpc_s2_score_means <- fpc_s2_scores_df %>% group_by(EID) %>% summarise(across(s2_fpc1_score:s2_fpc8_score, ~ mean(.x))) #colMeans - average loading by individual

#---
 #state 3 - 256 visitors

fpc_s3_scores_df <- data.frame(fpca_s3$scores)
names(fpc_s3_scores_df) <- c("fpc1_score","fpc2_score","fpc3_score","fpc4_score","fpc5_score","fpc6_score","fpc7_score","fpc8_score")
names(fpc_s3_scores_df)[1:8] <- paste0("s3_",names(fpc_s3_scores_df[1:8]))

# Add column with study IDs
EID_180_each <- rep(demog_health_states_df_915$EID,each=180)

fpc_s3_scores_df$EID <- EID_180_each[FHMM_915_index_s3]

fpc_s3_score_means <- fpc_s3_scores_df %>% group_by(EID) %>% summarise(across(s3_fpc1_score:s3_fpc8_score, ~ mean(.x))) #colMeans - average loading by individual

#---

# state 4 - 121  visitors

fpc_s4_scores_df <- data.frame(fpca_s4$scores)
names(fpc_s4_scores_df) <- c("fpc1_score","fpc2_score","fpc3_score","fpc4_score","fpc5_score","fpc6_score","fpc7_score","fpc8_score")
names(fpc_s4_scores_df)[1:8] <- paste0("s4_",names(fpc_s4_scores_df[1:8]))

# Add column with study IDs
EID_180_each <- rep(demog_health_states_df_915$EID,each=180)

fpc_s4_scores_df$EID <- EID_180_each[FHMM_915_index_s4]

fpc_s4_score_means <- fpc_s4_scores_df %>% group_by(EID) %>% summarise(across(s4_fpc1_score:s4_fpc8_score, ~ mean(.x))) #colMeans - average loading by individual


#--------




# LEFT JOIN ONTO demog_health_states_df_915
demog_health_states_fpcs_df_915 <- demog_health_states_df_915_fewer_outcomes

demog_health_states_fpcs_df_915 <- left_join(demog_health_states_fpcs_df_915,fpc_s1_score_means,by="EID")
demog_health_states_fpcs_df_915 <- left_join(demog_health_states_fpcs_df_915,fpc_s2_score_means,by="EID")
demog_health_states_fpcs_df_915 <- left_join(demog_health_states_fpcs_df_915,fpc_s3_score_means,by="EID")
demog_health_states_fpcs_df_915 <- left_join(demog_health_states_fpcs_df_915,fpc_s4_score_means,by="EID")

demog_health_states_fpcs_df_915 <- rename(demog_health_states_fpcs_df_915, "MFQ_SR_Total" = "MFQ_SR_Total..1")

view(demog_health_states_fpcs_df_915) # DA MASTER SHEET


names(demog_health_states_fpcs_df_915)



#save(demog_health_states_fpcs_df_915, file="demog_health_states_fpcs_df_915_080423")

load("demog_health_states_fpcs_df_915_080423")



```



# Multivariate BRMS for mental health & cognitive function scores 

(for subsets: >80% dominant?? OR? just dominant? OR? **visits at all?**) - probably visits at all makes most sense



# NEED TO RUN AGAIN BELOW
# is there a way to include state_percent without multicollinearity issues???

https://stats.stackexchange.com/questions/183601/interpreting-proportions-that-sum-to-one-as-independent-variables-in-linear-regr

```{r}
library(brms)

names(demog_health_states_fpcs_df_915)


#demog_health_states_fpcs_df_915 <- demog_health_states_fpcs_df_915 %>% rename(Cog_NIH7_Card = NIH7_Card,Cog_NIH7_Flanker = NIH7_Flanker,Cog_NIH7_List = NIH7_List,Cog_NIH7_Pattern = NIH7_Pattern)



# SET SEX TO BE FACTOR

#demog_health_states_fpcs_df_915$Sex <- as.factor(demog_health_states_fpcs_df_915$Sex)



#------

# State 1 (red)
s1_brms_df <- demog_health_states_fpcs_df_915 %>% filter(dominant_state==1) #(s2_percent >= 0.8)

mv_brms_s1_formula <- bf(mvbind(MFQ_SR_Total, SCARED_SR_Total, YSR_Ext_T, YSR_Int_T, Cog_NIH7_Card, Cog_NIH7_Flanker, Cog_NIH7_List, Cog_NIH7_Pattern) ~ Sex + Age + EHQ_Total + n_states_visited + n_transitions_all + dominant_proportion + s1_fpc1_score + s1_fpc2_score + s1_fpc3_score + s1_fpc4_score + s1_fpc5_score) +
  set_rescor(TRUE) #s1_percent + s2_percent + s3_percent + s4_percent +




fit_brm_s1 <- brm(mv_brms_s1_formula, data = s1_brms_df, iter=10000)

summary(fit_brm_s1)

save(fit_brm_s1,file="brms_s1_080423")
#load("brms_s1_080423")


#------

# State 2 (green)
s2_brms_df <- demog_health_states_fpcs_df_915 %>% filter(dominant_state==2) #(s2_percent >= 0.8)

mv_brms_s2_formula <- bf(mvbind(MFQ_SR_Total, SCARED_SR_Total, YSR_Ext_T, YSR_Int_T, Cog_NIH7_Card, Cog_NIH7_Flanker, Cog_NIH7_List, Cog_NIH7_Pattern) ~ Sex + Age + EHQ_Total + n_states_visited + n_transitions_all + dominant_proportion + s2_fpc1_score + s2_fpc2_score + s2_fpc3_score + s2_fpc4_score + s2_fpc5_score) +
  set_rescor(TRUE) #s1_percent + s2_percent + s3_percent + s4_percent +





fit_brm_s2 <- brm(mv_brms_s2_formula, data = s2_brms_df, iter=10000)

summary(fit_brm_s2)

save(fit_brm_s2,file="brms_s2_080423")
#load("brms_s2_080423")

#-------

# State 3 (orange)
s3_brms_df <- demog_health_states_fpcs_df_915 %>% filter(dominant_state==3) #(s2_percent >= 0.8)

mv_brms_s3_formula <- bf(mvbind(MFQ_SR_Total, SCARED_SR_Total, YSR_Ext_T, YSR_Int_T, Cog_NIH7_Card, Cog_NIH7_Flanker, Cog_NIH7_List, Cog_NIH7_Pattern) ~ Sex + Age + EHQ_Total + n_states_visited + n_transitions_all + dominant_proportion + s3_fpc1_score + s3_fpc2_score + s3_fpc3_score + s3_fpc4_score + s3_fpc5_score) +
  set_rescor(TRUE) #s1_percent + s2_percent + s3_percent + s4_percent +


fit_brm_s3 <- brm(mv_brms_s3_formula, data = s3_brms_df, iter=10000)

summary(fit_brm_s3)

save(fit_brm_s3,file="brms_s3_080423")
#load("brms_s3_080423")



#---------

# State 4 (blue)
s4_brms_df <- demog_health_states_fpcs_df_915 %>% filter(dominant_state==4) #(s2_percent >= 0.8)

mv_brms_s4_formula <- bf(mvbind(MFQ_SR_Total, SCARED_SR_Total, YSR_Ext_T, YSR_Int_T, Cog_NIH7_Card, Cog_NIH7_Flanker, Cog_NIH7_List, Cog_NIH7_Pattern) ~ Sex + Age + EHQ_Total + n_states_visited + n_transitions_all + dominant_proportion + s4_fpc1_score + s4_fpc2_score + s4_fpc3_score + s4_fpc4_score + s4_fpc5_score) +
  set_rescor(TRUE) #s1_percent + s2_percent + s3_percent + s4_percent +


fit_brm_s4 <- brm(mv_brms_s4_formula, data = s4_brms_df, iter=10000)

summary(fit_brm_s4)

save(fit_brm_s4,file="brms_s4_080423")
#load("brms_s4_080423")



#---------

# Load BRMS models

load("brms_s1_080423")
load("brms_s2_080423")
load("brms_s3_080423")
load("brms_s4_080423")


```



# BRMS models summarise in LaTeX tables

```{r}
library(modelsummary)

modelsummary(fit_brm_s1, output = "latex",mc.cores = 6,
             estimate = "{estimate}[{conf.low}, {conf.high}]",
             statistic=NULL,
            coef_omit = "Intercept")

modelsummary(fit_brm_s3, output = "latex",mc.cores = 6,
             estimate = "{estimate}[{conf.low}, {conf.high}]",
             statistic=NULL,
            coef_omit = "Intercept")

#-------

library(gtsummary)

tbl_regression(fit_brm_s1, exponentiate = F, intercept = F) %>% 
  gtsummary::as_gt() %>%
  gt::as_raw_html() #gt::as_latex()




tbl_regression(fit_brm_s3, exponentiate = F, intercept = F) %>% 
  gtsummary::as_gt() %>%
  gt::as_raw_html() 



# SUPPMATS
# state 2

tbl_regression(fit_brm_s2, exponentiate = F, intercept = F) %>% 
  gtsummary::as_gt() %>%
  gt::as_raw_html() 



# state 4
tbl_regression(fit_brm_s4, exponentiate = F, intercept = F) %>% 
  gtsummary::as_gt() %>%
  gt::as_raw_html() 

brms::bayes_R2(fit_brm_s4)
```















